The Importance of Affective States in Privacy Calculus

### 2021-05-03 submission.tex
relabeling findings for references

\subsection{Respondents' Privacy Concerns}
On average, respondents reported two privacy concerns of the five that were
suggested. The most common concern---password security---was three times as
popular than the least common concern---email tracking.

@@

\subsection{Ad Tracking}
A strong relationship exists such that \emph{the better an individual feels when
they delete cookies, the more frequently they delete them}. This was determined
by obtaining the gamma correlation value of magnitude .821 (p<.01,**) between
ordinal values for ``How often do you delete cookies on the device you most
regularly use for browsing?'' and ``How do you feel when you delete cookies?''.
Despite the strength of the relationship, the Chi-Square p-value of .178
indicates that the null hypothesis cannot be ruled out.

\subsection{Privacy and Social Media}

@@

\subsection{ISP Tracking Concerns and VPN Usage}
We exclude from our analyses one respondent who did not know what a VPN was.

>>>>

\subsection{Privacy Concerns} \label{Privacy Concerns}
On average, respondents reported two privacy concerns of the five that were
suggested. The most common concern---password security---was three times as
popular than the least common concern---email tracking.

@@

\subsection{Ad Tracking} \label{Ad Tracking}
A strong relationship exists such that \emph{the better an individual feels when
they delete cookies, the more frequently they delete them}. This was determined
by obtaining the gamma correlation value of magnitude .821 (p<.01,**) between
ordinal values for ``How often do you delete cookies on the device you most
regularly use for browsing?'' and ``How do you feel when you delete cookies?''.
Despite the strength of the relationship, the Chi-Square p-value of .178
indicates that the null hypothesis cannot be ruled out.

\subsection{Social Media} \label{Social Media}

@@

\subsection{VPN Usage (ISP Conerns)} \label{VPN Usage}
We exclude from our analyses one respondent who did not know what a VPN was.
